Prestige bias in cultural evolutionary dynamics

### 2024-05-08 ms/ms.tex
remove comments

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
% lines are also 300 simulations? why not markers? 
% what are error bars in C? CI 99%
% C x axis should say "Constant success-bias weight"
% A B x axis should say "Copier $i$; A y axis should be "Optimal success-bias weight, \alpha^*_i$.
}	
  \label{fig:influence_advantage}
\end{figure}

>>>>

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
}	
  \label{fig:influence_advantage}
\end{figure}
